Young children rationally integrate semantic and pragmatic information sources to infer the meaning of words

### 2020-08-31 paper/manuscript.Rmd
work on paper

When information integration in children is studied directly [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers], the focus is mostly on how children interpret an ambiguous referring expression in light of social-contextual information. In one of these studies [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it. The speaker, sitting on the opposite side of the display, saw only 3 of the compartments: the ball, the pen, and one of the glasses. When the speaker asked for "the glass", children had to integrate the semantics of the utterance with the perspective of the speaker to correctly infer which of the glasses - from their perspective - the speaker was referring to. This study, along with others, found that preschoolers use both information sources. What these studies do not do, however, is specify the process by which children integrate the different information sources. When discussing their results, authors refer to social-pragmatic theories of language use and learning [@grice1991studies; @sperber2001relevance; @clark1996using; @clark2009first; @tomasello2009constructing], all of which assume that information is integrated as part of a social inference process, but none of which clearly defines the process. As a consequence, we have no explicit and quantitative theory of how different information sources (and word learning mechanisms) are integrated.

@@

We focus on three information sources that play an integral part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children]. These inforamtion sources operate on different timescales: while (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development. This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word].

Our *rational integration model* arbitrates between information sources via Bayesian inference (see Fig. 1f for model formula). A listener ($L_{1}$) reasons about the referent of a speaker's ($S_{1}$) utterance. This reasoning is contextualized by the prior probability of each referent $\rho$ which we take to be a function of the common ground shared between the listener and the speaker. To decide between referents, the listener ($L_{1}$) reasons about what a rational speaker ($S_{1}$) with informativeness $\alpha$ would say given an intended referent. This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one. The informativity of each utterance is given by imagining which referent a listener, who interprets words according to their literal semantics (what we call a literal listener, $L_{0}$), would infer upon hearing the utterance. Naturally, this reasoning depends on what kind of semantic knowledge (for object j) $\theta$~j~ the speaker ascribes to the (literal) listener. Taken together, this model provides a quantitative theory of information integration during language learning. Furthermore, the model presents an explicit and substantive theory of development. It assumes that, while children’s sensitivity to the individual information sources increases with age, the way integration proceeds remains constant [@bohn2019pervasive; @bohn_tessler_merrick_frank_2019]. In the model, this is accomplished by making the parameters capturing sensitivity to speaker informativeness ($\alpha$~i~, Fig. 1d), the common ground ($\rho$~i~, Fig. 1c), and object specific semantic knowledge ($\theta$~i,j~, Fig. 1e) a function of the child’s age.

@@

To generate data to test the predictive and explanatory power of our model, we developed a world-learning paradigm in which we jointly manipulated the three information sources (Fig. 1). Children interacted on a tablet computer with a series of storybook speakers [@frank2016using]. The speakers used novel words (e.g., "wug") in the context of two potential referents. This situation is depicted in Fig. 1a iv, in which a speaker (here, a frog) appears with a known object (a duck, left) and an unfamiliar object (the diamond-shaped object, right). To identify the referent, the child could rely upon the three information sources described above. First, they may infer that a cooperative speaker would have used the word duck to refer to the known object (the duck); the fact that the speaker did not say duck then suggests that the speaker is most likely referring to a different object (the unfamiliar object). This basic inference is oftentimes referred to as a mutual exclusivity inference [@markman1988children; @halberda2003development]. More generally speaking, the listener can infer the referent of the novel word by assuming that the speaker is a rational agent who chooses the most informative words to refer to objects [@clark1987principle; @frank2014inferring]. Second, the child may rely upon what has already been established in the common ground with the speaker. Listeners expect speakers to communicate about things that are new to the common ground [@akhtar1996role; @diesendruck2004two]. Thus, the inference about the novel word referring to the unfamiliar object also depends on which object is new in context (Fig. 1a and b i-iii). Finally, the child may rely upon their previously acquired semantic knowledge, that is, how sure they are that the known object is called "duck". If the known object is something less familiar, such as a chess piece (e.g., a pawn), a 3-year-old child may draw a weaker inference, if they draw any inference at all [@lewis2020-me]. Taken together, the child has the opportunity to integrate their assumptions about (1) informative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge. In some versions of the experiment, some of these information sources were aligned (Fig. 1a) but in some they were in conflict (Fig. 1b).

@@

We tested the model in its ability to predict children’s actual behavior - at an age (between 2 and 5 years) at which they learn language at an exponential rate [@bloom2002children]. We estimated children’s (N=148) developing sensitivity to individual information sources in separate experiments (see Fig. 1c-e). We then generated parameter-free, quantitative, *a priori* model predictions (developmental trajectories) representing the model's expectations about how children should behave in a new situation in which all three information sources had to be integrated. We generated model predictions for 24 experimental conditions: 12 objects of different familiarities (requiring different levels of semantic knowledge), with novelty either conflicting or coinciding; Fig. 1. We compared these predictions to newly collected data from N = 220 children from the same age range. The results showed a very close alignment between model predictions and the data across the entire age range. That is, the average developmental trajectories predicted by the model resembled the trajectories found in the data (Fig. S6). For a more quantitative analysis, we binned predictions and data by year and correlated them. We found a high correlation showing that the model explained 79% of the variance in the data (Fig. 2a). These results seem to support the assumptions in the model that children integrate all available information sources. However, it is still possible that simpler models might make equally good or better predictions.

@@

The marginally less-complex *no word knowledge model* uses the same model architecture as the rational integration model. It takes in expectations about speaker informativeness and common ground, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge). That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.The *no common ground model* takes in object specific semantic knowledge and speaker informativeness but ignores common ground information. Instead of assuming that one object has a higher prior probability to be the referent because it is new in context, the speaker thinks that both objects are equally likely to be the referent. As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources. Finally, according to the *no speaker inforamtiveness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance. As a consequence, the inference is solely based on common ground expectations.

We found little support that children make inferences following one of the heuristic models. When using Bayesian model comparison via marginal likelihood of the data, [@lee2014bayesian], we find that the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Fig. 2). Taken together, we may conclude that children considered all available information sources.

@@

The fact that children integrated all the available information sources may be surprising, but does not rule out that the integration process itself might be different from the one described in the rational integration model. Remember that this model assumes that all information sources enter into an integrated inference process. However, a more modular view seems equally plausible: children might compute separate inferences based on a subset of the available information and then integrate them by weighting them according to some ratio. This view would allow for the possibility that some information sources are considered to be more important than others. In other words, children might be biased towards some information sources (e.g. a 60:40 ratio). We formalized this alternative view as a *biased integration model*. This model assumes that semantic knowledge and expectations about speaker informativeness enter into one inference (mutual exclusivity inference [@markman1988children; @lewis2020-me; @clark1987principle]) while common ground information enters into a second one. The outcome of both processes are then weighted according to the parameter $\phi$. Like the rational integration model, this model takes in all available information sources in an age sensitive way and assumes that they are integrated - the integration process itself, however, is construed in a different way.

@@

The rational integration model assumes that the integration process itself does not change with age [@bohn2019pervasive]. That is, while children's sensitivity to each information source develops, the way they relate to one another remains the same. An alternative perspective would be to assume that the integration process itself changes with age. The biased integration model provides a way to think about developmental change in the integration process: Children are biased towards some information sources, but this bias itself changes with age. We formalize such an alternative view as a *developmental bias model* which is structurally identical to the biased integration model but in which the parameter $\phi$ changes with age. The model assumes that the importance of the different information sources changes with age.

@@

The developmental bias model explains a substantial portion of the variance in the data (Fig. 3c). The estimated developmental trajectory for the bias parameter $\phi$ suggests that younger children put a higher emphasis on common ground information, while older children rely more on the mutual exclusivity inference (Fig. 3d). The relative importance of the two inferences seems to switch at around 3 years. Yet again, when we directly compare the competitor models, we find that the data is several orders of magnitude more likely under the rational integration model (Fig. 3). Interestingly, when we compared the rational integration model with its parameters not constrained by the experimental data (i.e. the "pure" prediction model described above), it also outperformed both bias models (see Fig. S10 and Tab. S6). Taken together, these results show that the integration process is best described as fully integrated and stable over time.

@@

We found that this rational integration model made accurate quantitative predictions across a range of experimental conditions - in some of which information sources were aligned, in some of which they were in conflict. Predictions from the model better explained the data compared to lesioned models - which assumed that children ignore one of the information sources - suggesting that children used all available information.

To test the explanatory power of the model - how well it explains the process by which information is integrated - we formalized an alternative, modular, view. According to the biased integration model, children use all available information sources but compute separate inferences based on a subset of them. Integration happens by weighting the outcomes of these separate inferences by some ratio. By allowing the ratio to be in favor of one of the inferences, this model captures the idea that children might be biased to some information sources over others. Even though such a model made reasonable predictions, we found that the rational integration model explained children's behavior much more accurately. Finally, we tested an alternative view on the development of the integration process. According tot the developmental bias model, the importance of the different information sources changed with age. Again, the rational integration model provided a much better fit to the data, suggesting that the integration process remains stable over time.

@@

There are multiple ways in which the model and the experiments presented here could be extended. First, it would be important to replicate our findings in a more diverse sample, that is, with children from a different cultural background who learn a different language. In such a study, we would not expect that our results replicate in a strict sense - that is, we would not expect to see the same developmental trajectories in all cultures and/or languages. Substantial variation is much more likely. Our computational model provides a way to think about how to reconcile cross-cultural variation with a universal cognitive architecture: We expect differences in how sensitive children are to the individual information sources at different ages, but similarities in how information is integrated [@bohn2019pervasive]. In computational terms, we assume a universal architecture that specifies the relation between a set of parameters with varying values.

Second, it would be useful to flesh out the cognitive processes that underlie reasoning about common ground. In its current form, our model does not specify how the listener arrives at the expectation that some objects are more likely referents given previous interactions with the speaker. We assume that common ground changes speaker's expectations about what are likely referents [@hanna2003effects] and measured these expectations to inform the parameter values in our model. Computationally, the model does not differentiate between common ground information and other reasons that might make an object contextually more salient. A good starting point to address this issue could be work that formalizes reasoning about common ground as trading-off between (differing) perspectives [@heller2016perspective; @mozuraitis2018modeling].

@@

A more detailed description of the experiments and the models can be found in the supplementary material. The experimental procedure, sample size and analysis for each experiment was pre-registered (https://osf.io/7rg9j/registrations). Experimental procedures, model and analysis scripts can be found in an online repository (https://github.com/manuelbohn/spin). Experiment 1 and 2 were designed to estimate children's developing sensitivity to each information source. Their results inform he parameter values in the model (see Fig. 1). Experiment 3 was designed to test how children integrate the different information sources.

@@

Across three experiments, a total of `r length(unique(me_data$subid)) + length(unique(prior_data$subid)) + length(unique(comb_data$subid))` children participated. Experiment 1 involved `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls). Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1).

>>>>

When information integration is studied directly, the focus is mostly on how children interpret an ambiguous referring expression in light of social-contextual information [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers]. In one of these studies [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it. The speaker, sitting on the opposite side of the display, saw only 3 of the compartments: the ball, the pen, and one of the glasses. When the speaker asked for "the glass", children had to integrate the semantics of the utterance with the perspective of the speaker to correctly infer which of the glasses - from their perspective - the speaker was referring to. This study, along with others, found that preschoolers use both information sources. What these studies do not do, however, is specify the process by which children integrate the different information sources. When discussing their results, authors refer to social-pragmatic theories of language use and learning [@grice1991studies; @sperber2001relevance; @clark1996using; @clark2009first; @tomasello2009constructing], all of which assume that information is integrated as part of a social inference process, but none of which clearly defines the process. As a consequence, we have no explicit and quantitative theory of how different information sources (and word learning mechanisms) are integrated.

@@

We focus on three information sources that play an integral part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using; @clark2015common], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children]. These information sources operate on different timescales: while (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development. This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word].

Our *rational integration model* arbitrates between information sources via Bayesian inference (see Fig. 1f for model formula). A listener ($L_{1}$) reasons about the referent of a speaker's ($S_{1}$) utterance. This reasoning is contextualized by the prior probability of each referent $\rho$ -- which we take to be a function of the common ground shared between the listener and the speaker. To decide between referents, the listener ($L_{1}$) reasons about what a rational speaker ($S_{1}$) with informativeness $\alpha$ would say given an intended referent. This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one. The informativity of each utterance is given by imagining which referent a listener, who interprets words according to their literal semantics (what we call a literal listener, $L_{0}$), would infer upon hearing the utterance. Naturally, this reasoning depends on what kind of semantic knowledge (for object j) $\theta$~j~ the speaker ascribes to the (literal) listener. Taken together, this model provides a quantitative theory of information integration during language learning. Furthermore, the model presents an explicit and substantive theory of development. It assumes that, while children’s sensitivity to the individual information sources increases with age, the way integration proceeds remains constant [@bohn2019pervasive; @bohn_tessler_merrick_frank_2019]. In the model, this is accomplished by making the parameters capturing sensitivity to speaker informativeness ($\alpha$~i~, Fig. 1d), the common ground ($\rho$~i~, Fig. 1c), and object specific semantic knowledge ($\theta$~i,j~, Fig. 1e) a function of the child’s age.

@@

To test the predictive and explanatory power of our model, we developed a world-learning paradigm in which we jointly manipulated the three information sources (Fig. 1). Children interacted on a tablet computer with a series of storybook speakers [@frank2016using]. The speakers used novel words (e.g., "wug") in the context of two potential referents. This situation is depicted in Fig. 1a iv, in which a speaker (here, a frog) appears with a known object (a duck, left) and an unfamiliar object (the diamond-shaped object, right). To identify the referent, the child could rely upon the three information sources described above. First, they may infer that a cooperative speaker would have used the word "duck" to refer to the known object (the duck); the fact that the speaker did not say duck then suggests that the speaker is most likely referring to a different object (the unfamiliar object). This basic inference is oftentimes referred to as a mutual exclusivity inference [@markman1988children; @halberda2003development]. More generally speaking, the listener can infer the referent of the novel word by assuming that the speaker is a rational agent who chooses the most informative words to refer to objects [@clark1987principle; @frank2014inferring]. Second, the child may rely upon what has already been established in the common ground with the speaker. Listeners expect speakers to communicate about things that are new to the common ground [@akhtar1996role; @diesendruck2004two]. Thus, the inference about the novel word referring to the unfamiliar object also depends on which object is new in context (Fig. 1a and b i-iii). Finally, the child may rely upon their previously acquired semantic knowledge, that is, how sure they are that the known object is called "duck". If the known object is something less familiar, such as a chess piece (e.g., a pawn), a 3-year-old child may draw a weaker inference, if they draw any inference at all [@lewis2020-me]. Taken together, the child has the opportunity to integrate their assumptions about (1) informative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge. In some versions of the experiment, some of these information sources were aligned (Fig. 1a) but in some they were in conflict (Fig. 1b).

@@

We tested the model in its ability to predict children’s actual behavior - at an age (between 2 and 5 years) at which they learn language at an exponential rate [@bloom2002children]. We estimated children’s (N=148) developing sensitivity to individual information sources in separate experiments (Experiment 1 and 2) (see Fig. 1c-e). We then generated parameter-free, quantitative, *a priori* model predictions (developmental trajectories) representing the model's expectations about how children should behave in a new situation in which all three information sources had to be integrated. We generated model predictions for 24 experimental conditions: 12 objects of different familiarities (requiring different levels of semantic knowledge), with novelty either conflicting or coinciding; Fig. 1. We compared these predictions to newly collected data from N = 220 children from the same age range (Experiment 3). The results showed a very close alignment between model predictions and the data across the entire age range. That is, the average developmental trajectories predicted by the model resembled the trajectories found in the data (Fig. S6). For a more quantitative analysis, we binned predictions and data by year and correlated them. We found a high correlation, with the model explaining 79% of the variance in the data (Fig. 2a). These results seem to support the assumptions in the model that children integrate all available information sources. However, it is still possible that simpler models might make equally good -- or even better -- predictions.

@@

The *no word knowledge model* uses the same model architecture as the rational integration model. It takes in expectations about speaker informativeness and common ground, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge). That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge. The *no common ground model* takes in object specific semantic knowledge and speaker informativeness but ignores common ground information. Instead of assuming that one object has a higher prior probability to be the referent because it is new in context, the speaker thinks that both objects are equally likely to be the referent. As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources. Finally, according to the *no speaker inforamtiveness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance. As a consequence, the inference is solely based on common ground expectations.

We found little support that children make inferences following one of the heuristic models (Fig. 2b). When using Bayesian model comparison via marginal likelihood of the data, [@lee2014bayesian], we find that the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Fig. 2). Taken together, we may conclude that children considered all available information sources.

@@

The fact that children integrated all the available information sources may be surprising, but does not rule out that the integration process itself might be different from the one described in the rational integration model. Remember that this model assumes that all information sources enter into an integrated inference process. However, a more modular view seems equally plausible: children might compute separate inferences based on a subset of the available information and then integrate them by weighting them according to some ratio. This view would allow for the possibility that some information sources are considered to be more important than others. In other words, children might be biased towards some information sources. We formalized this alternative view as a *biased integration model*. This model assumes that semantic knowledge and expectations about speaker informativeness enter into one inference (mutual exclusivity inference [@markman1988children; @lewis2020-me; @clark1987principle]) while common ground information enters into a second one. The outcome of both processes are then weighted according to the parameter $\phi$. Like the rational integration model, this model takes in all available information sources in an age sensitive way and assumes that they are integrated - the integration process itself, however, is construed in a different way.

@@

The rational integration model assumes that the integration process itself does not change with age [@bohn2019pervasive]. That is, while children's sensitivity to each information source develops, the way they relate to one another remains the same. An alternative perspective would be to assume that the integration process itself changes with age. The biased integration model provides a way to think about developmental change in the integration process: Children are biased towards some information sources, but the bias itself changes with age. We formalize such an alternative view as a *developmental bias model* which is structurally identical to the biased integration model but in which the parameter $\phi$ changes with age. The model assumes that the importance of the different information sources changes with age.

@@

The developmental bias model explains a substantial portion of the variance in the data (Fig. 3c). The estimated developmental trajectory for the bias parameter $\phi$ suggests that younger children put a higher emphasis on common ground information, while older children rely more on the mutual exclusivity inference (Fig. 3d). The relative importance of the two inferences seems to switch at around age 3. Yet again, when we directly compare the competitor models, we find that the data is several orders of magnitude more likely under the rational integration model (Fig. 3). Interestingly, when we compared the rational integration model with its parameters not constrained by the experimental data (i.e. the "pure" prediction model described above), it also outperformed both bias models (see Fig. S10 and Tab. S6). Taken together, these results show that the integration process is best described as fully integrated and stable over time.

@@

We found that this rational integration model made accurate quantitative predictions across a range of experimental conditions - in some of which information sources were aligned, in some of which they were in conflict. Predictions from the model better explained the data compared to lesioned models which assumed that children ignore one of the information sources, suggesting that children used all available information.

To test the explanatory power of the model - how well it explains the process by which information is integrated - we formalized an alternative, modular, view. According to the biased integration model, children use all available information sources but compute separate inferences based on a subset of them. Integration happens by weighting the outcomes of these separate inferences by some ratio. By allowing the ratio to be in favor of one of the inferences, this model captures the idea that children might be biased to some information sources over others. Even though such a model made reasonable predictions, we found that the rational integration model explained children's behavior much more accurately. Finally, we tested an alternative view on the development of the integration process. According to the developmental bias model, the importance of the different information sources changed with age. Again, the rational integration model provided a much better fit to the data, suggesting that the integration process remains stable over time.

@@

There are multiple ways in which the model and the experiments presented here could be extended. First, it would be important to replicate our findings in a more diverse sample, that is, with children from a different cultural background who learn a different language. In such a study, we would not expect that our results replicate in a strict sense; that is, we would not expect to see the same developmental trajectories in all cultures and/or languages. Substantial variation is much more likely. Our computational model provides a way to think about how to reconcile cross-cultural variation with a universal cognitive architecture: We expect differences in how sensitive children are to the individual information sources at different ages, but similarities in how information is integrated [@bohn2019pervasive]. In computational terms, we assume a universal architecture that specifies the relation between a set of varying parameters.

Second, it would be useful to flesh out the cognitive processes that underlie reasoning about common ground. In its current form, our model does not specify how the listener arrives at the expectation that some objects are more likely referents because they are new in common ground. We assume that common ground changes speaker's expectations about what are likely referents [@hanna2003effects] and measured these expectations to inform the parameter values in our model. Computationally, the model does not differentiate between common ground information and other reasons that might make an object contextually more salient. A good starting point to address this issue could be work that formalizes reasoning about common ground as trading-off between (differing) perspectives [@heller2016perspective; @mozuraitis2018modeling].

@@

A more detailed description of the experiments and the models can be found in the supplementary material. The experimental procedure, sample size and analysis for each experiment were pre-registered (https://osf.io/7rg9j/registrations). Experimental procedures, model and analysis scripts can be found in an online repository (https://github.com/manuelbohn/spin). Experiment 1 and 2 were designed to estimate children's developing sensitivity to each information source. Their results inform he parameter values in the model (see Fig. 1 c-f). Experiment 3 was designed to test how children integrate the different information sources.

@@

Across the three experiments, a total of `r length(unique(me_data$subid)) + length(unique(prior_data$subid)) + length(unique(comb_data$subid))` children participated. Experiment 1 involved `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls). Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1).
